Balsa: A Compact Line Notation Based on SMILES

### 2022-07-03 manuscript.tex
Adds figure for invalid uses of configurational descriptors. Closes #16

A central atom whose parity attribute assumes a non-default value must have either four bonds if no virtual hydrogens are present, or three bonds if one virtual hydrogen is present. Some topologies might appear to be similar enough that the \ttt{parity} attribute can be used, but they all must be reported as errors. Examples include the central atom of allenes and other odd cumulenes, and the sulfur atom of sulfoxides where the lone pair is misconstrued as a substituent.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Invalid uses of configurational descriptors. Only configuration about four-coordinate tetrahedral atoms is supported.}
    \label{fig:invalid-configurational-descriptors}
\end{figure}

>>>>

A central atom whose parity attribute assumes a non-default value must have either four bonds if no virtual hydrogens are present, or three bonds if one virtual hydrogen is present. Some topologies might appear to be similar enough that the \ttt{parity} attribute can be used, but they all must be reported as errors (Figure~\ref{fig:invalid-atom-parity}). Examples include the central atom of allenes and other odd cumulenes, and the sulfur atom of sulfoxides where the lone pair is misconstrued as a substituent.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{invalid-atom-parity.pdf}
    \caption{Invalid uses of atom parity. Only configuration about tetrasubstituted, tetrahedral atoms is supported. The marked atoms (cyan background) lack four substituents, tetrahedral geometry, or both. Assigning a non-default atom parity to any of them would be an error.}
    \label{fig:invalid-atom-parity}
\end{figure}
